---
title: "MSDR"
author: "Magdy Laban"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MSDR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(msdr)
```

# NOAA Earthquakes Capstone
This Package is the final project for mastering software development in R specialization on Coursera and the major of this package is to make a package that cleans up and visualizes the NOAA earthquakes data .

# The Full Process
## Reading and cleaning the data
* you can read the data through the following example : 
```{r read_data, eval=FALSE}
NOAA <- read.delim("signif.txt")
```
* you can clean the data through two methods :
```{r clean_date,eval=FALSE}
NOAA %>%
eq_data_clean()
```
```{r add_location,eval=FALSE}
NOAA %>%
eq_location_clean()
```

## Data Visualization 
1.this section is for creating a new geoms for ggplot2 , there are two geoms 

* `geom_timeline()` : this ends up with a timeline geom that represents the earthquakes for a specific period of date .
```{r geom_timeline,eval=FALSE}
noaa %>%
    eq_clean_data()%>%
    filter(YEAR >= 2000, COUNTRY == "USA") %>%
    ggplot(aes(x = DATE, size = as.numeric(EQ_PRIMARY), color = as.numeric(TOTAL_DEATHS)))+
    geom_timeline()
```
* `geom_timeline_label()` : this ends up with a timeline geom that represents the earthquakes for a specific period of date and a label that shows up the location name where the earthquake has happend .
```{r geom_timeline_label, eval=FALSE}
noaa %>%
    eq_clean_data() %>%
    eq_location_clean() %>%
    filter(YEAR >= 2000, COUNTRY == "USA") %>%
    ggplot(aes(x = DATE, size = as.numeric(EQ_PRIMARY),color = as.numeric(TOTAL_DEATHS), label = LOCATION)) +
    geom_timeline() +
    geom_timeline_label()
```
2.there are also two leaflet based methods 

* `eq_map()` : this method used to represent the location of each earthquakes on a leaflet map .
```{r eq_map,eval=FALSE}
noaa %>%
    eq_clean_data() %>%
    dplyr::filter(COUNTRY == "MEXICO" & lubridate::year(DATE) >= 2000) %>%
    eq_map(annot_col = "DATE")
```
* `eq_create_label()` : this method used to cearte a pop-up that contains the information about the earthquakes 
```{r eq_create_data,eval=FALSE}
noaa %>%
    eq_clean_data() %>%
    dplyr::filter(COUNTRY == "MEXICO" & lubridate::year(DATE) >= 2000) %>%
    dplyr::mutate(popup_text = eq_create_label(.)) %>%
    eq_map(annot_col = "popup_text")
```
